---
title: "Intro to foofactors"
author: "Alex Peterson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to foofactors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Welcome to foofactors, for all your factor needs!

Foofactors contains four functions: fbind, fcheck, forder, and freq_out. 

fbind() allows you to bind factors together logically, compare:

```{r}
#install_github("alex-peterson/foofactors")
library(foofactors)

c(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])      #a bunch of numbers
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])  #what you actually want
```

freq_out() produces a frequency table for your factors:

```{r}
freq_out(iris$Species)
```


fcheck() lets you know if you have a factor vector that really should be a character vector. 
It returns a logical value: "TRUE" if everything's okay, "FALSE" if there is only one instance of
each factor level. 

```{r}
x <- as.factor(c("a", "a", "b", "c", "c", "c"))
y <- as.factor(c("a", "b", "c", "d", "e", "f"))

fcheck(x)
fcheck(y)
```


Finally, forder() allows you to reorder your factors based on a summary statistic of a quantitative
variable, either descending or ascending. 

```{r}
iris$Species <- forder(iris$Species, iris$Sepal.Width, desc = TRUE)
boxplot(Sepal.Width ~ Species, data = iris)

ChickWeight$Diet <- forder(ChickWeight$Diet, ChickWeight$weight, desc = FALSE)
boxplot(weight ~ Diet, data = ChickWeight)

```

Ta-da! Now all your factor problems are solved forever with no problems. 
